\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-13 paper/main.tex
minor changes

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  \sloppy
  AI-enabled applications are prolific today. Deep Learning~(DL)
  libraries, such as \torch{} and \tf{}, provide the building
  blocks for the AI components of these applications. As any piece of
  software, these libraries can be buggy.
  %% and those bugs can affect a
  %% great deal of applications using those libraries.
  An impressive number of bug-finding techniques to address this
  problem have been proposed, but the lack of a curated set of
  reproducible bugs in DL libraries hinders credible evaluation of these
  techniques. We present \tname, a database of curated reproducible
  bugs to fill that gap.
  %% enable credible  evaluation of bug-finding DL library testing techniques.
  Our dataset currently consists of \numbugs{} environments to
  reproduce bugs across three popular DL libraries, namely, \jax,
  \tf, and \torch.
\textbf{Screencast}:~\url{https://tinyurl.com/BugsInDLLs}  
\end{abstract}

@@

This paper presents \tname, a database of curated reproducible bugs to
enable credible evaluation of DL library testing techniques. \tname\ is
equipped with a command-line interface to enable researchers to analyze
and reproduce bug instances.

@@

\tname\ contains \numbugs{} instances of reproducible bugs
representing three popular DL libraries, namely, \jax, \tf, and
\torch. Table~\ref{table:bug-characterization} shows the list of bug
instances for each supported library. Column ``\#'' shows the number
of bug instances, column ``build'' shows the breakdown of instances
based on the kind of build, and column ``environment'' shows the
breakdown of instances based on the kind of environment to reproduce
the bug.

@@

\textbf{Libraries.}~\torch~and \tf are popular DL libraries
intensively used in the literature. \jax\ is a newer library that has
been rapidly gaining popularity. All these libraries are open source
with active communities supporting their maintenaance.

@@

\textbf{Bugs.}~We focused on bug reports that have been accepted by
the developer community as true bugs. We determine this by checking
whether the bugs have appropriate labels and have been fixed with pull
requests linked to them. Among these confirmed bug reports, we choose
the ones that have enough information to reproduce the bugs, i.e.,
code to reproduce the bug, enviroment required for
reproduction\Fix{Abid, can you confirm that environment here is not
  the same as venv-docker that we are using on Table 1? instead it
  means the version of CUDA, libraries, etc.? If so, avoid using the
  word environment.}, clear description of the desired behavior,
etc. Once we can successfully reproduce the bug by creating the
enviroment detailed in the report, we choose the bug to be included in
our dataset.

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  \sloppy
  AI-enabled applications are prolific today. Deep Learning~(DL)
  libraries, such as \torch{} and \tf{}, provide the building
  blocks for the AI components of these applications. As any piece of
  software, these libraries can be buggy.
  %% and those bugs can affect a
  %% great deal of applications using those libraries.
  An impressive number of bug-finding techniques to address this
  problem have been proposed, but the lack of a curated set of
  reproducible bugs in DL libraries hinders credible evaluation of these
  techniques. We present \tname, a database of curated reproducible
  bugs to fill that gap.
  %% enable credible  evaluation of bug-finding DL library testing techniques.
  Our dataset currently consists of \numbugs{} environments to
  reproduce bugs across three popular DL libraries, namely, \jax,
  \tf, and \torch.
\textbf{Screencast}:~\url{https://tinyurl.com/BugsInDLLs}\\
\textbf{GitHub repository}:~\url{https://github.com/ncsu-swat/bugsindlls}    
\end{abstract}

@@

We present \tname, a database of curated reproducible bugs to
enable credible evaluation of DL library testing techniques. \tname\ is
equipped with a command-line interface to enable researchers to analyze
and reproduce bug instances.

@@

\tname\ contains \numbugs{} instances of reproducible bugs
representing three popular DL libraries, namely, \jax, \tf, and
\torch. Table~\ref{table:bug-characterization} shows the list of bug
instances for each supported library. Column ``\#'' shows the number
of bug instances, column ``build'' shows the breakdown of instances
for each kind of build, and column ``environment'' shows the breakdown
of instances for each kind of environment to reproduce the bug.

@@

\textbf{Libraries.}~\torch~and \tf are popular DL libraries
intensively used in the literature. \jax\ is a newer library that has
been rapidly gaining popularity. All these libraries are open source
with active communities supporting their maintenance.

@@

\textbf{Bugs.}~We focused on bug reports that have been accepted by
the developer community as true bugs. We determine this by checking
whether the bugs have appropriate labels and have been fixed with pull
requests linked to them. Among these confirmed bug reports, we choose
the ones that have enough information to reproduce the bugs, i.e.,
code to reproduce the bug, enviroment required for
reproduction\Fix{Abid, can you confirm that environment here is not
  the same as venv-docker that we are using on Table 1? instead it
  means the version of CUDA, libraries, etc.? If so, avoid (re)using the
  word environment.}, clear description of the desired behavior,
etc. Once we can successfully reproduce the bug by creating the
enviroment detailed in the report, we choose the bug to be included in
our dataset.
